---
title: "Bayesian Statistics - Project"
output: html_notebook
---



```{r warning=FALSE, message=FALSE}
setwd("~/Semester 10/Bayes/Project")

library(tidyverse)
library(rstan)
library(ggimage)
library(bayesplot)
library(loo)
library(patchwork)

data <- readRDS("penguins.RDS")

```

# EDA

```{r warning=FALSE, message=FALSE}

data %>%
  summarise(mean_bl = mean(bill_length), sd_bl = sd(bill_length),
            min = min(bill_length), max = max(bill_length),
             n = n())
data %>%
  group_by(species) %>%
  summarise(mean_bl = mean(bill_length), sd_bl = sd(bill_length),
             min = min(bill_length), max = max(bill_length),
             n = n())


data %>%
  group_by(species, sex) %>%
  summarise(mean_bl = mean(bill_length), sd_bl = sd(bill_length),
             min = min(bill_length), max = max(bill_length),
            n = n())

```


```{r}

ggplot(data, aes(x=bill_length,fill=sex)) +
  geom_histogram(alpha=0.5,position = "identity") +
  facet_wrap(~ species, scales = "fixed") +   
  labs(title = "Distribution of Penguin Bill Length by Species",
       x = "Bill Length", y = "Count",fill="Sex") +
  theme_classic() +
  theme(strip.text = element_text(face = "bold", size = 12)) 

```

```{r}


h <- hist(data$bill_length,breaks = 40,plot = FALSE)

img_data <- map2_df(
  seq_along(h$counts),h$counts,\(i, n) {
    tibble(x = h$mids[i],y = seq_len(n))
  })

img_data$image <- "~/Semester 10/Bayes/Project/penguin.png"

ggplot(img_data, aes(x, y)) +
  geom_bar(data=data.frame(h$counts,h$mids),aes(x=h.mids,y=h.counts),inherit.aes = FALSE,stat="identity") +
  geom_image(aes(image = image, y = y - 0.5),size = 0.04) +
  labs(title = "Distribution of Penguin Bill Length",x = "Bill Length",y = "Count") +
  theme_classic()

```


```{r}

h_list <- data %>%
  group_by(species) %>%
  group_map(~ {
    h <- hist(.x$bill_length, breaks = 15, plot = FALSE)
    map2_df(
      seq_along(h$counts), h$counts, \(i, n) {
        tibble(x = h$mids[i], y = seq_len(n))
      }) %>%
      mutate(species = .y$species)
  }) %>%
  bind_rows()

# Add species-specific images
h_list <- h_list %>%
  mutate(image = case_when(
    species == "Adelie"    ~ "~/Semester 10/Bayes/Project/penguin_red.png",
    species == "Chinstrap" ~ "~/Semester 10/Bayes/Project/penguin_blue.png",
    species == "Gentoo"    ~ "~/Semester 10/Bayes/Project/penguin_yellow.png"
  ))

# Bar data per species
bar_list <- data %>%
  group_by(species) %>%
  group_map(~ {
    h <- hist(.x$bill_length, breaks = 15, plot = FALSE)
    tibble(mids = h$mids, counts = h$counts, species = .y$species)
  }) %>%
  bind_rows()

ggplot(h_list, aes(x, y)) +
  geom_bar(data = bar_list, aes(x = mids, y = counts),
           inherit.aes = FALSE, stat = "identity", fill = "grey80", color = "grey60") +
  geom_image(aes(image = image, y = y - 0.5), size = 0.035) +
  facet_wrap(~ species, scales = "fixed") + 
  labs(title = "Distribution of Penguin Bill Length by Species",
       x = "Bill Length", y = "Count") +
  theme_classic() +
  theme(strip.text = element_text(face = "bold", size = 12))

```


```{r}

data$image <- case_when(
  data$species == "Adelie" ~ "~/Semester 10/Bayes/Project/penguin_red.png",
  data$species == "Chinstrap" ~ "~/Semester 10/Bayes/Project/penguin_blue.png",
  data$species == "Gentoo" ~ "~/Semester 10/Bayes/Project/penguin_yellow.png"
)

ggplot(data, aes(x = bill_depth, y = bill_length)) +
  geom_point(aes(color = species, shape = sex),alpha = 0,size = 6) +
  scale_color_manual(values = c(Adelie = "red4",Chinstrap = "blue4",Gentoo = "gold3")) +
  guides(color = guide_legend(override.aes = list(alpha = 0.8, size = 5))) +
  geom_point(aes(shape = sex),size = 6) +
  geom_image(aes(image=image),alpha = 0.7, size = 0.03) +
  labs(title = "Bill Length vs. Bill Depth",x="Bill Depth",y="Bill Length",shape="Sex",color="Species") +
  theme_classic()
```



# Models

Use the values of the fitted lm for the priors.

```{r}

summary(lm(bill_length~bill_depth+sex+species,data))
summary(lm(bill_length~bill_depth+sex,data[data$species=="Adelie",]))
summary(lm(bill_length~bill_depth+sex,data[data$species=="Chinstrap",]))
summary(lm(bill_length~bill_depth+sex,data[data$species=="Gentoo",]))

```



```{r}
data$sex_num <- ifelse(data$sex == "male", 1, 0)
data$species_num <- as.integer(data$species)

stan_data <- list(
  N          = nrow(data),
  K          = 3,
  species    = data$species_num,
  bill_depth = data$bill_depth,
  bill_depth2 = data$bill_depth^2,
  sex        = data$sex_num,
  bill_length = data$bill_length,
  log_bill_length = log(data$bill_length)
)

```

# Seperate Model

For the seperate model types I compare two models. One is a normal model and one a student-t model.

Weakly informative but empirical motivated priors are being used.

## 3 species - normal

Priors:
alpha ~ normal(28,10);
beta_depth ~ normal(0.5,1);
beta_sex ~ normal(3,1);
sigma ~ normal(0,5);



```{r}

model_code <- "
data {
  int<lower=0> N;
  int<lower=1> K;
  array[N] int<lower=1, upper=K> species;
  vector[N] bill_depth;
  array[N] int<lower=0, upper=1> sex;
  vector[N] bill_length;
}

parameters {
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;
  vector<lower=0>[K] sigma;
}

model {
  alpha ~ normal(28,10);
  beta_depth ~ normal(0.5,1);
  beta_sex   ~ normal(3,1);
  sigma ~ normal(0,5);

  for (n in 1:N) {
    int k = species[n];

    bill_length[n] ~ normal(
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {
  vector[N] log_lik;
  vector[N] y_rep;

  for (n in 1:N) {
    int k = species[n];

    real mu_n =
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n];

    log_lik[n] =
      normal_lpdf(bill_length[n] | mu_n, sigma[k]);

    y_rep[n] =
      normal_rng(mu_n, sigma[k]);
  }
}"

sepN <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=7000,seed=984232)
```



## 3 species - t

Priors:
alpha ~ normal(28,10);
beta_depth ~ normal(0.5,1);
beta_sex ~ normal(3,1);
sigma ~ normal(0,5);

nu ~ gamma(2,0.1);


```{r}

model_code <- "
data {
  int<lower=0> N;
  int<lower=1> K; 
  array[N] int<lower=1, upper=K> species;
  vector[N] bill_depth;
  array[N] int<lower=0, upper=1> sex;
  vector[N] bill_length;
}

parameters {
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;
  vector<lower=0>[K] sigma;
  real<lower=2> nu;   
}

model {
  alpha ~ normal(28,10);
  beta_depth ~ normal(0.5,1);
  beta_sex   ~ normal(3,1);
  sigma ~ normal(0,5);
  nu ~ gamma(2,0.1);
  
  for (n in 1:N) {
    int k = species[n];
    bill_length[n] ~ student_t(
      nu,
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {
  vector[N] log_lik;
  vector[N] y_rep;
  for (n in 1:N) {
    int k = species[n];
    real mu_n = alpha[k]
              + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n];
              
    log_lik[n] = student_t_lpdf(bill_length[n] | nu, mu_n, sigma[k]);
    y_rep[n]   = student_t_rng(nu, mu_n, sigma[k]);
  }
}"


sepT <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=7000,seed=984232)
```

## Compare those two models

```{r}
list_of_draws <- rstan::extract(sepN)
y_pred <- list_of_draws$y_rep

p1 <- ppc_dens_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated kernel density")
p2 <- ppc_ecdf_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated CDF")
p3 <- ppc_stat_2d(stan_data$bill_length, y_pred, stat=c("min","max")) + labs(title="Empirical and simulated minimum and maximum values")
(p1+p2)/p3

list_of_draws <- rstan::extract(sepT)
y_pred <- list_of_draws$y_rep


p1 <- ppc_dens_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated kernel density")
p2 <- ppc_ecdf_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated CDF")
p3 <- ppc_stat_2d(stan_data$bill_length, y_pred, stat=c("min","max")) + labs(title="Empirical and simulated minimum and maximum values")
(p1+p2)/p3

```


# Hierarchical Model

Because for the seperate case, the student t model was a better fit. A hierarchical student t model is the next step.

Priors: 
mu_alpha ~ normal(28,5);
mu_depth ~ normal(0.5,1);
mu_sex ~ normal(3,1);

tau_alpha ~ exponential(1);
tau_depth ~ exponential(1);
tau_sex ~ exponential(1);

sigma ~ exponential(1);

nu ~ gamma(2,0.1);

```{r}


model_code <- "data {
  int<lower=0> N;
  int<lower=1> K;

  array[N] int<lower=1, upper=K> species;
  array[N] int<lower=0, upper=1> sex;

  vector[N] bill_depth;
  vector[N] bill_length;
}

parameters {

  // group-level parameters
  real mu_alpha;
  real mu_depth;
  real mu_sex;

  real<lower=0> tau_alpha;
  real<lower=0> tau_depth;
  real<lower=0> tau_sex;

  // species-level parameters
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;

  vector<lower=0>[K] sigma;

  real<lower=2> nu;
}

model {

  // hyperpriors
  mu_alpha ~ normal(28, 5);
  mu_depth ~ normal(0.5, 1);
  mu_sex   ~ normal(3, 1);

  tau_alpha ~ exponential(1);
  tau_depth ~ exponential(1);
  tau_sex   ~ exponential(1);

  // hierarchical priors
  alpha ~ normal(mu_alpha, tau_alpha);
  beta_depth ~ normal(mu_depth, tau_depth);
  beta_sex ~ normal(mu_sex, tau_sex);

  sigma ~ exponential(1);

  nu ~ gamma(2, 0.1);

  // likelihood
  for (n in 1:N) {

    int k = species[n];

    bill_length[n] ~ student_t(
      nu,
      alpha[k]
      + beta_depth[k] * bill_depth[n]
      + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {

  vector[N] log_lik;
  vector[N] y_rep;

  for (n in 1:N) {

    int k = species[n];

    real mu_n =
      alpha[k]
      + beta_depth[k] * bill_depth[n]
      + beta_sex[k] * sex[n];

    log_lik[n] =
      student_t_lpdf(
        bill_length[n] |
        nu,
        mu_n,
        sigma[k]
      );

    y_rep[n] =
      student_t_rng(
        nu,
        mu_n,
        sigma[k]
      );
  }
} "



hierT <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=10000,seed=984232)
```


```{r}
list_of_draws <- rstan::extract(hierT)
y_pred <- list_of_draws$y_rep


p1 <- ppc_dens_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated kernel density")
p2 <- ppc_ecdf_overlay(data$bill_length, y_pred[1:200,]) + labs(title="Empirical and simulated CDF")
p3 <- ppc_stat_2d(stan_data$bill_length, y_pred, stat=c("min","max")) + labs(title="Empirical and simulated minimum and maximum values")
(p1+p2)/p3
```



# Convergence Checks


```{r}

p1 <- mcmc_rhat_hist(bayesplot::rhat(sepN))+labs(title="Seperate Model - Normal")
p2 <- mcmc_rhat_hist(bayesplot::rhat(sepT))+labs(title="Seperate Model - Student t")
p3 <- mcmc_rhat_hist(bayesplot::rhat(hierT))+labs(title="Hierarchical Model")

rhat_1 <- bayesplot::rhat(sepN)[1:12]
mcmc_rhat(rhat_1)+yaxis_text(hjust=0)
rhat_2 <- bayesplot::rhat(sepT)[1:13]
mcmc_rhat(rhat_2)+yaxis_text(hjust=0)
rhat_3 <- bayesplot::rhat(hierT)[1:19]
mcmc_rhat(rhat_3)+yaxis_text(hjust=0)

```


```{r}
p1 <- traceplot(sepN,names(rhat_1))+labs(title="Seperate Model - Normal")
p2 <- traceplot(sepT,names(rhat_2))+labs(title="Seperate Model - Student t")
p3 <- traceplot(hierT,names(rhat_3))+labs(title="Hierarchical Model")

(p1+p2)/p3

```


```{r}
p1 <- mcmc_neff_hist(neff_ratio(sepN))+labs(title="Seperate Model - Normal")
p2 <- mcmc_neff_hist(neff_ratio(sepT))+labs(title="Seperate Model - Student t")
p3 <- mcmc_neff_hist(neff_ratio(hierT))+labs(title="Hierarchical Model")

(p1+p2)/p3
```

```{r}
check_hmc_diagnostics(sepN)
check_hmc_diagnostics(sepT)
check_hmc_diagnostics(hierT)
```



# Model comparison

## PSIS-LOO

```{r}


(loo_normal <- loo(extract_log_lik(sepN)))
(loo_t      <- loo(extract_log_lik(sepT)))
(loo_hier  <- loo(extract_log_lik(hierT)))

loo_compare(loo_normal, loo_t, loo_hier)
```

## WAIC

```{r}

waic(extract_log_lik(sepN))
waic(extract_log_lik(sepT))
waic(extract_log_lik(hierT))


```

# Prior Sensitivity Analysis

## 3 species - normal

Weaker priors are chosen to compare the estimates

Priors:
alpha ~ normal(28,20);
beta_depth ~ normal(0,3);
beta_sex ~ normal(0,5);
sigma ~ normal(0,10);



```{r}

model_code <- "
data {
  int<lower=0> N;
  int<lower=1> K;
  array[N] int<lower=1, upper=K> species;
  vector[N] bill_depth;
  array[N] int<lower=0, upper=1> sex;
  vector[N] bill_length;
}

parameters {
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;
  vector<lower=0>[K] sigma;
}


model {
  alpha ~ normal(28,20);
  beta_depth ~ normal(0,3);
  beta_sex   ~ normal(0,5);
  sigma ~ normal(0,10);

  for (n in 1:N) {
    int k = species[n];

    bill_length[n] ~ normal(
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {
  vector[N] log_lik;
  vector[N] y_rep;

  for (n in 1:N) {
    int k = species[n];

    real mu_n =
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n];

    log_lik[n] =
      normal_lpdf(bill_length[n] | mu_n, sigma[k]);

    y_rep[n] =
      normal_rng(mu_n, sigma[k]);
  }
}"

sepN_SA <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=7000,seed=984232)
```

```{r}
d1 <- mcmc_intervals_data(
  as.array(sepN),
  pars = c(
    "alpha[1]","alpha[2]","alpha[3]",
    "beta_depth[1]","beta_depth[2]","beta_depth[3]",
    "beta_sex[1]","beta_sex[2]","beta_sex[3]"
  )
)

d1$model <- "Original"

d2 <- mcmc_intervals_data(
  as.array(sepN_SA),
  pars = c(
    "alpha[1]","alpha[2]","alpha[3]",
    "beta_depth[1]","beta_depth[2]","beta_depth[3]",
    "beta_sex[1]","beta_sex[2]","beta_sex[3]"
  )
)

d2$model <- "Weak"

d <- bind_rows(d1, d2)

ggplot(d, aes(y = parameter, x = m, color = model)) +
  geom_errorbarh(aes(xmin = ll, xmax = hh),
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_errorbarh(aes(xmin = l, xmax = h),
                 size = 1.2,
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_point(position = position_dodge(width = 0.6),
             size = 2) +
  labs(
    x = "Posterior estimate",
    y = NULL,
    color = "Model",
    title = "Separate Gaussian"
  ) +
  theme_minimal()
```


## 3 species - t

Priors:
alpha ~ normal(28,20);
beta_depth ~ normal(0,3);
beta_sex ~ normal(0,5);

sigma ~ normal(0,10);

nu ~ gamma(2,0.05);

```{r}

model_code <- "
data {
  int<lower=0> N;
  int<lower=1> K; 
  array[N] int<lower=1, upper=K> species;
  vector[N] bill_depth;
  array[N] int<lower=0, upper=1> sex;
  vector[N] bill_length;
}

parameters {
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;
  vector<lower=0>[K] sigma;
  real<lower=2> nu;   
}

model {
  alpha ~ normal(28,20);
  beta_depth ~ normal(0,3);
  beta_sex   ~ normal(0,5);
  sigma ~ normal(0,10);
  nu ~ gamma(2,0.05);
  
  for (n in 1:N) {
    int k = species[n];
    bill_length[n] ~ student_t(
      nu,
      alpha[k] + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {
  vector[N] log_lik;
  vector[N] y_rep;
  for (n in 1:N) {
    int k = species[n];
    real mu_n = alpha[k]
              + beta_depth[k] * bill_depth[n] + beta_sex[k] * sex[n];
              
    log_lik[n] = student_t_lpdf(bill_length[n] | nu, mu_n, sigma[k]);
    y_rep[n]   = student_t_rng(nu, mu_n, sigma[k]);
  }
}"


sepT_SA <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=7000,seed=984232)
```

```{r}
d1 <- mcmc_intervals_data(
  as.array(sepT),
  pars = c(
    "alpha[1]","alpha[2]","alpha[3]",
    "beta_depth[1]","beta_depth[2]","beta_depth[3]",
    "beta_sex[1]","beta_sex[2]","beta_sex[3]"
  )
)

d1$model <- "Original"

d2 <- mcmc_intervals_data(
  as.array(sepT_SA),
  pars = c(
    "alpha[1]","alpha[2]","alpha[3]",
    "beta_depth[1]","beta_depth[2]","beta_depth[3]",
    "beta_sex[1]","beta_sex[2]","beta_sex[3]"
  )
)

d2$model <- "Weak"

d <- bind_rows(d1, d2)

ggplot(d, aes(y = parameter, x = m, color = model)) +
  geom_errorbarh(aes(xmin = ll, xmax = hh),
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_errorbarh(aes(xmin = l, xmax = h),
                 size = 1.2,
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_point(position = position_dodge(width = 0.6),
             size = 2) +
  labs(
    x = "Posterior estimate",
    y = NULL,
    color = "Model",
    title = "Separate Student-t"
  ) +
  theme_minimal()

```


## Hierarchical Model

Priors:

mu_alpha ~ normal(28, 10)
mu_depth ~ normal(0, 3)
mu_sex   ~ normal(0, 5)

tau_alpha ~ exponential(0.5)
tau_depth ~ exponential(0.5)
tau_sex   ~ exponential(0.5)

sigma ~ exponential(0.5)

nu ~ gamma(2, 0.05)

```{r}


model_code <- "data {
  int<lower=0> N;
  int<lower=1> K;

  array[N] int<lower=1, upper=K> species;
  array[N] int<lower=0, upper=1> sex;

  vector[N] bill_depth;
  vector[N] bill_length;
}

parameters {

  // group-level parameters
  real mu_alpha;
  real mu_depth;
  real mu_sex;

  real<lower=0> tau_alpha;
  real<lower=0> tau_depth;
  real<lower=0> tau_sex;

  // species-level parameters
  vector[K] alpha;
  vector[K] beta_depth;
  vector[K] beta_sex;

  vector<lower=0>[K] sigma;

  real<lower=2> nu;
}

model {

  // hyperpriors
  mu_alpha ~ normal(28, 10);
  mu_depth ~ normal(0, 3);
  mu_sex   ~ normal(0, 5);

  tau_alpha ~ exponential(0.5);
  tau_depth ~ exponential(0.5);
  tau_sex   ~ exponential(0.5);

  // hierarchical priors
  alpha ~ normal(mu_alpha, tau_alpha);
  beta_depth ~ normal(mu_depth, tau_depth);
  beta_sex ~ normal(mu_sex, tau_sex);

  sigma ~ exponential(0.5);

  nu ~ gamma(2, 0.05);

  // likelihood
  for (n in 1:N) {

    int k = species[n];

    bill_length[n] ~ student_t(
      nu,
      alpha[k]
      + beta_depth[k] * bill_depth[n]
      + beta_sex[k] * sex[n],
      sigma[k]
    );
  }
}

generated quantities {

  vector[N] log_lik;
  vector[N] y_rep;

  for (n in 1:N) {

    int k = species[n];

    real mu_n =
      alpha[k]
      + beta_depth[k] * bill_depth[n]
      + beta_sex[k] * sex[n];

    log_lik[n] =
      student_t_lpdf(
        bill_length[n] |
        nu,
        mu_n,
        sigma[k]
      );

    y_rep[n] =
      student_t_rng(
        nu,
        mu_n,
        sigma[k]
      );
  }
} "



hierT_SA <- stan(model_code=model_code,data=stan_data,
             chains=4,iter=10000,seed=984232)
```


```{r}

d1 <- mcmc_intervals_data(
  as.array(hierT),
  pars = dimnames(as.array(hierT))[[3]][1:19]
)

d1$model <- "Original"

d2 <- mcmc_intervals_data(
  as.array(hierT_SA),
  pars =dimnames(as.array(hierT))[[3]][1:19]
)

d2$model <- "Weak"

d <- bind_rows(d1, d2)

ggplot(d, aes(y = parameter, x = m, color = model)) +
  geom_errorbarh(aes(xmin = ll, xmax = hh),
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_errorbarh(aes(xmin = l, xmax = h),
                 size = 1.2,
                 height = 0,
                 position = position_dodge(width = 0.6)) +
  geom_point(position = position_dodge(width = 0.6),
             size = 2) +
  labs(
    x = "Posterior estimate",
    y = NULL,
    color = "Model",
    title = "Hierarchical Student-t"
  ) +
  theme_minimal()


```



## Model comparison


```{r}


(loo_normal <- loo(extract_log_lik(sepN_SA)))
(loo_t      <- loo(extract_log_lik(sepT_SA)))
(loo_hier  <- loo(extract_log_lik(hierT_SA)))

loo_compare(loo_normal, loo_t, loo_hier)
```


# Software comparison: brms


```{r}
library(brms)


brm_hierT <- brm(
  bill_length ~ bill_depth + sex + (1 + bill_depth + sex | species),
  data   = data,
  family = student(),
  chains = 4, iter = 10000, warmup = 5000,
  control = list(adapt_delta = 0.95),
  seed=984232
)
```

